---
title: "Part_tati"
author: "Tetyana Drobot"
date: '5 декабря 2017 г '
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 2. Beauty of the data

There are many ways to represent and analyse the data sets, we decided to explore the beauty of our Reddit dataset in several ways. After extracting sentiment from each word in the title sentence using Saif & Turney (2010) research for NRC dictionary (as research was named after National research Council Canada), which allocates a word into eight sentiment categories. At first, we used a 'visNetwork' library to  create a node-based radial dendrogram. It requires creation of the hierarchy, so we modified our initial sentiment dataset with additional column containing the following hierarchy: Sentiment | Sentiment Detail | Word. The following diagram shows the sentiment allocation for the words used in top 50 posts. 


```{r cars}
"Radial_NRC_Visual.html"
```

Secondly, just as in real life there are multiple interpretations, a single word is allocated to the multiple sentiments. To explore this further we create an interactive network, which portrays connections between words and sentiment. Indeed, as seen on the graph below, a single word may be allocated to the multiple sentiments. The emotions associated with either positive or negative sentiment are grouped together, only a "surprise" node is located in the middle linking the words associated with both.


```{r pressure, echo=FALSE}
"Network_NRC_Visual.html"
```



References: 

Saif, M.M. & Turney, P.D. (June, 2010). Emotions Evoked by Common Words and Phrases: Using Mechanical Turk to Create an Emotion Lexicon. Proceedings of the NAACL-HLT 2010 Workshop on Computational Approaches to Analysis and Generation of Emotion in Text. LA, California.  
